TrueSkill Through Time: the \proglang{Julia}, \proglang{Python} and \proglang{R} packages

### 2021-04-09 article.tex
TTT: manejor correcto de las fechas en figura y códigos-tex

\en{The success of the TrueSkill solution~\citep{Herbrich2007} is based on the usage of an efficient method for computing the Gaussian distribution that guarantees the approximation of the posterior~(see section~\ref{sec:approximate_posterior}),}

@@

\en{The approach adopted by TrueSkill to treat the dynamical process, known as \emph{filtering}, uses the approximate posterior as the prior for the next event.}
\es{El enfoque adoptado por TrueSkill para tratar el proceso din\'amico, conocido como \emph{filtering}, usa el posterior aproximado como prior del siguiente evento.}
\en{The approximate posterior at any given time is:}
\es{Luego, el posterior aproximado en un determinado momento es,}

@@

\en{The total runtimes for initialization of the \texttt{History} class and the \texttt{convergenc()} method were,}
\es{Los tiempos totales de inicialización de la clase \texttt{History} y del método  \texttt{convergenc()} fueron,}

@@

\subsection{\en{The history of the Association of Tennis Professionals (ATP)}\es{Historia de la Asociación de Tenistas Profesionales (ATP)}} \label{sec:appendix_atp_code}
%
\begin{lstlisting}[backgroundcolor=\color{python},caption={\en{\proglang{Python} code}\es{Código \proglang{Python}}},aboveskip=0.0 \baselineskip, belowskip=0.1cm]
import pandas as pd
df = pd.read_csv('input/history.csv', low_memory=False)

columns = zip(df.w1_id, df.w2_id, df.l1_id, df.l2_id, df.double)
composition = [[[w1,w2],[l1,l2]] if d == 't' else [[w1],[l1]] for w1, w2, l1, l2, d in columns ]

tour_time = pd.to_datetime(df.time_start,format='%Y-%m-%d')
base_time = pd.to_datetime('1910-01-01',format='%Y-%m-%d')
times =  (tour_time-base_time).dt.days - df.round_number

h = History(composition = composition, times = times, sigma = 1.6, gamma = 0.036)
h.convergence(epsilon=0.01, iterations=10)
\end{lstlisting}
%
\begin{lstlisting}[backgroundcolor=\color{r},caption={\en{\proglang{R} code}\es{Código \proglang{R}}},aboveskip=0.0 \baselineskip, belowskip=0.1cm]

data = read.csv("input/history.csv", header=T)
get_composition = function(x){
    res = list()
    if (x["double"]=="t"){
        res[[1]] = c(x["w1_name"],x["w2_name"])
        res[[2]] = c(x["l1_name"],x["l2_name"])
    }else{
        res[[1]] = c(x["w1_name"])
        res[[2]] = c(x["l1_name"])
    }
    return(res)
}
composition =  apply(data, 1, get_composition ) 
times = as.Date(data[,"time_start"], format = "%Y-%m-%d")
times = times - as.Date("1910-01-01", format = "%Y-%m-%d")
times = as.numeric(times )

h = History(composition = composition, times = times, sigma = 1.6, gamma = 0.036)
h$convergence(epsilon=0.01, iterations=10)
\end{lstlisting}

>>>>

\en{The success of the TrueSkill solution~\citep{Herbrich2007} is based on the usage of an efficient method for computing the Gaussian distribution that best approximate the exact posterior~(see section~\ref{sec:approximate_posterior}),}

@@

\en{The approach adopted by TrueSkill to treat the dynamical process, known as \emph{filtering}, uses the last approximate posterior as the prior for the next event.}
\es{El enfoque adoptado por TrueSkill para tratar el proceso din\'amico, conocido como \emph{filtering}, usa el último posterior aproximado como prior del siguiente evento.}
\en{The approximate posterior at any given time is defined as:}
\es{Luego, el posterior aproximado en un determinado momento se define como,}

@@

\en{The total runtimes for initialization of the \texttt{History} class and the \texttt{convergence()} method were,}
\es{Los tiempos totales de inicialización de la clase \texttt{History} y del método  \texttt{convergence()} fueron,}

@@

\subsection{\en{The history of the Association of Tennis Professionals (ATP)}\es{Historia de la Asociación de Tenistas Profesionales (ATP)}} \label{sec:appendix_atp_code}
%
\begin{lstlisting}[backgroundcolor=\color{python},caption={\en{\proglang{Python} code}\es{Código \proglang{Python}}},aboveskip=0.0 \baselineskip, belowskip=0.1cm]
import pandas as pd; from datetime import datetime
df = pd.read_csv('input/history.csv')

columns = zip(df.w1_id, df.w2_id, df.l1_id, df.l2_id, df.double)
composition = [[[w1,w2],[l1,l2]] if d=='t' else [[w1],[l1]] for w1, w2, l1, l2, d in columns]
days = [ datetime.strptime(t, "%Y-%m-%d").timestamp()/(60*60*24) for t in df.time_start]

h = History(composition = composition, times = days, sigma = 1.6, gamma = 0.036)
h.convergence(epsilon=0.01, iterations=10)
\end{lstlisting}
%
\begin{lstlisting}[backgroundcolor=\color{r},caption={\en{\proglang{R} code}\es{Código \proglang{R}}},aboveskip=0.0 \baselineskip, belowskip=0.1cm]
data = read.csv("input/history.csv", header=T)

get_composition = function(x){
    res = list()
    if (x["double"]=="t"){
        res[[1]] = c(x["w1_name"],x["w2_name"])
        res[[2]] = c(x["l1_name"],x["l2_name"])
    }else{
        res[[1]] = c(x["w1_name"])
        res[[2]] = c(x["l1_name"])
    }
    return(res)
}
composition =  apply(data, 1, get_composition ) 
days = as.numeric(as.Date(data[,"time_start"], format = "%Y-%m-%d"))

h = History(composition = composition, times = days, sigma = 1.6, gamma = 0.036)
h$convergence(epsilon=0.01, iterations=10)
\end{lstlisting}
